Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2013-03-27 tex/ms.tex
reflow paragraph I am about to delete and rewrite
partial introduction outline; its now a huge mess

>>>>

Telescopes don't make catalogs, they make images (Hogg \& Lang 20xx).
Nonetheless, some of the most important astronomical projects have produced
enormously productive catalogs (the \textsl{SDSS}, for examle CITATION).
There is a growing understanding that precise measurements
of astronomical sources have to be made directly 
in the imaging data
(CITE Lang, Anderson, something in weak lensing):
It is impossible to pass the full information content of the imaging to the end user
via a catalog (which by necessity is built with point estimates of the quantities of
interest).

...time domain seems simple, because only photometry matters!

...but catalogs make censored point estimates, usually... noise, morphology, CRs, defects...

...catalogs could be better if they did forced photometry.  upper limits worse.
nulls worse.  total obfuscation worst of all

...here we are going to work with nulls; they can still be informative!

...as an example, consider \figurename~\ref{fig:example}...
